%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
% 
% Updated by: Armin Hadzic
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{burgundy} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.88, 
			lmargin=0.95cm, 
			rmargin=0.95cm, 
			footnotesep=1.5cm
			]{geometry} % Reduce document margins

%bibliograph content
\usepackage[minnames=8,
			maxnames=10,
			backend=bibtex,
            style=authoryear,
            natbib=true, 
            style=numeric-comp,
            sorting=ydnt,
            backref=false,
            defernumbers=true
            ]{biblatex}
\usepackage{booktabs}
\usepackage[unicode,
			colorlinks=true,
			urlcolor=blue,
			]{hyperref}

% Publication bib files
\addbibresource{publications/conferences}
\addbibresource{publications/journals}
\addbibresource{publications/workshops}
%\addbibresource[label=under_review]{under_review}
%\addbibresource[label=abstracts]{abstracts}


%Title spacing
\makeatletter
\patchcmd{\makehead}{%search
    \ifthenelse{\equal{\@title}{}}{}{\titlestyle{~|~\@title}}\\%
    }{%replace
    \ifthenelse{\equal{\@title}{}}{}{\titlestyle{~|~\@title}}\\[0.25cm]%
  }{%success
  }{%failure
  }
\makeatother

% Remove bullet from contact information, replace with 2 spaces
\renewcommand*{\makeheaddetailssymbol}{~~}

%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Armin} % Your first name
\familyname{Hadzic} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum  LaTeX Error: Missing \begin{document}.Vitae}
%\address{}
%\mobile{(\#\#\#) \#\#\#-\#\#\#\#}

\email{firstlast at outlook.com}

% The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\homepage{www.arminhadzic.com}
\social[linkedin][www.linkedin.com/in/armin-hadzic]{LI}
\social[googlescholar][scholar.google.com/citations?user=DlDme3IAAAAJ&hl=en]{Publications}

%----------------------------------------------------------------------------------------


\begin{document}

\makecvtitle % Print the CV title
\vspace*{-1.5cm}

%----------------------------------------------------------------------------------------
%   RESEARCH INTERESTS SECTION
%----------------------------------------------------------------------------------------
\section{Research Interests}

\cvitem{}{I am interested in developing unsupervised learning methods to address challenges in \textbf{open vocabulary segmentation} and \textbf{latent information representation}, with a focus on multi-modal learning (e.g., imagery, text, and point clouds). My research centers on \textbf{multi-modal fusion}, generative models for \textbf{image synthesis}, and \textbf{localization}. I am particularly interested in how deep learning can drive \textbf{scalable} AI systems that integrate diverse data modalities for advanced machine perception and AI-driven decision making applications.}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{Advisor: Nathan Jacobs}{Master of Science in Computer Science}{University of Kentucky}{2018-2020}{\textit{GPA -- 4.0}}{Thesis: Estimating Free-Flow Speed with LiDAR and Overhead Imagery}
\cventry{}{Bachelor of Science in Computer Engineering}{University of Kentucky}{2016}{\textit{GPA -- 3.8}}{Graduated Magna Cum Laude}
\cventry{}{Bachelor of Science in Electrical Engineering}{University of Kentucky}{2009-2013}{\textit{GPA -- 3.8}}{Graduated Magna Cum Laude, Minor in Computer Science}  % Arguments not required can be left empty



%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}
\subsection{Research}
\cventry{Fairfax, VA}{\textsc{DZYNE Technologies Inc.}}{AI Research Scientist}{2021-Present}{}
{
\begin{itemize} 
	\item Led research efforts in \textbf{multi-modal fusion}~\cite{greenwell2024watch}, \textbf{pose estimation}, \textbf{localization}, \textbf{depth estimation}, and \textbf{image synthesis}~\cite{Low2High}, advancing AI-driven models for multi-modal learning, contextual representation~\cite{ProbTraffic}, and scalable perception systems.
	\item Developed and implemented scalable supervised and unsupervised learning algorithms for multi-modal data integration and contextual understanding, enabling advanced applications in autonomous systems, interactive AI, and real-time simulations.
	\item Contributed to 9 successful proposals (SBIR, STTR, BAA), securing \textbf{\$3M in funding} from IARPA and NGA, driving innovation in advanced AI technologies.
\end{itemize}
}
\cventry{Laurel, MD}{\textsc{Johns Hopkins University Applied Physics Laboratory}}{AI Research Scientist}{2020-2021}{}
{
\begin{itemize} 
	\item Designed neural network bias reduction methods for skin disease classification and segmentation~\cite{yuan2023edgemixup, paul2022tara}.
	\item Developed methods for optimizing multi-agent swarm control systems based on computational neuroscience~\cite{hadzic2022100218, buckley2021interdisciplinary}.
	\item Integrated geospatial products into artificial neural networks for high resolution building damage classification, structure localization, and green house gas regression~\cite{mukherjee2021towards}.  
\end{itemize}
}
\cventry{Lexington, KY}{\textsc{UK Computer Vision Lab}}{Research Assistant}{2018-2020}{}
{
\begin{itemize} 
	\item Advised by Professor Nathan Jacobs.
	\item Designed multi-modal neural networks~\cite{RasterNetpaper, chen2021safety} to leverage point clouds and satellite imagery to estimate free-flow speeds of roads from a birds-eye-view.
	\item Developed Natural Language Processing (NLP) temporal convolutional and attention-based neural network models to estimate firm economic performance using public SEC text reports. 
\end{itemize}
}
\cventry{Laurel, MD}{\textsc{Johns Hopkins University Applied Physics Laboratory}}{Machine Perception Intern}{2019}{}
{
\begin{itemize} 
	\item Advised by Ryan Mukherjee and Dr. Gordon Christie.
	\item Developed methods for regressing population of displaced communities for disaster relief efforts, utilizing overhead imagery and deep neural networks~\cite{DCApaper}.
\end{itemize}
}
\cventry{Lexington, KY}{\textsc{UK Computer Vision Lab}}{Volunteer Machine Learning Research Assistant}{2017-2018}{}
{
\begin{itemize} 
	\item Automated the US Road Assessment Program (usRAP) road safety assessment using a deep convolutional neural network~\cite{WACVpaper} to directly estimate roadway safety based on street-level panorama images, reducing evaluation time to milliseconds per image.
	\item Integrated the roadway safety estimator into a GPS vehicle routing system to enhance navigation with the capability to identify a balanced, safe and fast, driving route.
\end{itemize}
}

%------------------------------------------------

\subsection{Industry}

\cventry{Lexington, KY}{\textsc{Belcan Engineering Group Inc.}}{Software Development Engineer}{2017-2018}{}
{
	\begin{itemize}
		\item Developed, maintained, and tested a jet engine diagnostic and fault resolution system, saving over \$100,000 by automating engine maintenance diagnostics.
		\item Integrated and streamlined a legacy cross-platform build system with modern development tools, mitigating build errors and reducing development time.
	\end{itemize}
}

%------------------------------------------------

\cventry{Lexington, KY}{\textsc{Belcan Engineering Group Inc.}}{Embedded Software Engineer}{2016-2017}{}
{
\begin{itemize}
	\item Streamlined the user interface and reduced diagnostic time of jet engines by identifying, isolating, and purging Onboard Maintenance System inefficiencies and defects.
\end{itemize}
}

%------------------------------------------------

\cventry{Lexington, KY}{\textsc{Belcan Engineering Group Inc.}}{Software Test Engineer}{2015-2016}{}
{
\begin{itemize}
	\item Designed and implemented Control and Diagnostic System Verification and Validation Tests for 4 P\&W Turbofan Jet Engines. 
	\item Discovered mission critical control logic, software, and documentation defects through root-cause analysis, informal testing, regression testing and system testing; leading to best in class, safe, and high performance jet engines.
\end{itemize}
}

%------------------------------------------------

\cventry{Lexington, KY}{\textsc{Tempur Sealy International Inc}}{Software Engineering Co-op}{2013-2014}{}
{
\begin{itemize}
	\item Pioneered and developed a GUI and 3D topography mapping application to visually analyze large datapoint datasets, generating streamlined product testing, seamless user experience, and refined product quality.
\end{itemize}
}
%------------------------------------------------

\cventry{Florence, KY}{\textsc{Johnson Controls Inc}}{Software Engineering Intern}{2012}{}
{
\begin{itemize}
	\item Designed and implemented a software algorithm for streamlined Automated Guided Vehicle (AGV) routing, saving \$57,000 per year in scrap reduction and transportation costs.
\end{itemize}
}

%----------------------------------------------------------------------------------------
%   PUBLICATIONS SKILLS SECTION
%----------------------------------------------------------------------------------------

\printbibheading [title={Publications}]
\printbibliography[
    title={Conference Papers},
    keyword={conferences},
    heading=subbibliography, 
    resetnumbers=false]
\printbibliography[
    title={Journal Articles},
    keyword={journals},
    heading=subbibliography, 
    resetnumbers=false]
\printbibliography[
    title={Workshop Papers},
    keyword={workshops}, 
    heading=subbibliography, 
    resetnumbers=false]

%----------------------------------------------------------------------------------------
%   TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Technical Skills}

\begin{tabular}{l@{\qquad}|>{\hspace{0.5pc}}l@{\qquad}} % The final bracket specifies the number of columns in the table along with left and right borders which are specified using vertical bars (|); each column can be left, right or center-justified using l, r or c. To specify a precise width, use p{width}, e.g. p{5cm}.  The qquads specify verticle line dividers. hspace is used to specify the space between text and verticle dividers.

%\toprule % Top horizontal line

Languages \& Frameworks		& \textbf{Python}, C/C++, Java, Verilog, \LaTeX, Shell, \textbf{PyTorch}, Scikit-Learn, Keras \\ \hline % row 1 Tensorflow
Artificial Intelligence 	& \textbf{Multimodal Fusion}, \textbf{Transformers}, LLMs, Reinforcement Learning, SSL \\ \hline % row 2 Distillation
Computer Vision 			& Generative AI, Segmentation, 3D, Localization, Pose, Depth, Remote Sensing\\ \hline % row 3
Infrastructure 				& Data Processing, Distributed Training, Slurm, Docker, Optimization, Evaluation \\ \hline % row 4
Auxiliary 					& Research, Metrics, Presentation, Technical Writing, Publication, Mentorship \\ % row 5

\end{tabular}

%----------------------------------------------------------------------------------------
%   SERVICE SECTION
%----------------------------------------------------------------------------------------

\section{Service \& Recognition}
\cvitem{}{
\subsection{Technical Committee}
\begin{itemize}
\item 2021 University of Maryland Honor's program Gemstone thesis defense.
\end{itemize}
\subsection{Program Committee/Reviewing}
\begin{itemize}
\item CVPR: 2023, 2024, 2025
\begin{itemize}
	\item Outstanding Reviewer 2024, 2025
\end{itemize}
\item ECCV: 2022, 2024
\item ICCV: 2023
\item ICLR: 2024
\item NeurIPS: 2023, 2024
\item WACV Round 1 and 2: 2023, 2024, 2025
\item CVPR Workshop EARTHVISION: 2022, 2023
\end{itemize}
\subsection{Awards}
\begin{itemize}
\item{}{Computer Science Outstanding MS Student 2020.}
\item{}{Dean's List Fall 2010 to Spring 2013.}
\end{itemize}
}

\end{document}
